Analysis of the \\ Information Security Job Landscape \\ in Austria

### 2020-05-29 paper/paper.tex
Fix spelling.

The second most common requirement is an apprenticeship (Ausbildung) at around 36\%, followed by the Matura with 22\%. After a manual review of the 4\% belonging to apprenticeship (Lehre), these seem to be mostly false positives, at least in our case when only taking information security jobs into account.

>>>>

The second most common requirement is an apprenticeship (“\german{Ausbildung}”) at around 36\%, followed by the Matura with 22\%. After a manual review of the 4\% belonging to apprenticeship (“\german{Lehre}”), these seem to be mostly false positives, at least in our case when only taking information security jobs into account.
